%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{report} %report allows for chapters
\renewcommand\thesection{\arabic{section}} % ignore the title number for sections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{color, soul, xcolor} % Colored text and highlighting, respectively

%Tikz
\usepackage{tikz-cd} % For commutative diagrams
\usepackage{tikz-3dplot}
\RequirePackage{pgfplots}
\usetikzlibrary{shadows}
\usetikzlibrary{shapes}
\usetikzlibrary{decorations}
\usetikzlibrary{arrows,decorations.markings} 
\usetikzlibrary{quotes,angles}

\usepackage{mathtools}
\usepackage{answers}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{mathrsfs}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{marvosym,wasysym} %fucking smileys
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Shortcuts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Number systems
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}

% Operators/functions
\newcommand{\id}{\mathrm{Id}}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\csch}{csch}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Environments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Italic font
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{axiom}{Axiom}

% Plain font
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{solution}{Solution}[section]
\newtheorem{problem}{Problem}[section]
\newtheorem{question}{Question}[section]
\newtheorem{answer}{Answer}[section]
\newtheorem{exercise}{Exercise}[section]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}


\begin{center}
   \textsc{\large MATH 255, Homework 9}\\
\end{center}
\vspace{.5cm}

\noindent\textbf{Problem 1.} Write the following as a differential equation:

\emph{The rate of change of an animal population grows proportionally to the current population times the difference of the current population from the maximum population.}

This equation you will write models the population dynamics of many biological systems that breed and compete for food.
\vspace*{.5cm}

\noindent\textbf{Problem 2.} Show that 
\[
f(t)=te^{t}+e^t
\]
solves the differential equation
\[
f'(t)=f(t)+e^t.
\]
\vspace*{.5cm}

\noindent\textbf{Problem 3.} The change in position $x(t)$ of a particle follows the ODE
\[
x'(t)=tx
\]
and satisfies the initial condition $x(0)=1$.  Find the exact solution to this ODE.
\vspace*{.5cm}

\noindent\textbf{Problem 4.} Consider the simple predator-prey ($x$ is predator, $y$ is prey) interaction model given by
\begin{align*}
    x'(t) &= Ax+ B y\\
    y'(t) &= -C x + Dy
\end{align*}
where $A,B,C,$ and $D$ are all positive constants.
\begin{enumerate}[(a)]
    \item Write in words what the equation for $x'$ is describing.
    \item Write in words what the equation for $y'$ is describing.
    \item Note that this equation is linear.  So write the pair of coupled equations as a single vector-matrix equation
    \[
    \mathbf{v}'(t) = M\mathbf{v}(t).
    \]
\end{enumerate}

\noindent\textbf{Problem 5.} Consider the following second order linear differential equation
\[
f''(t)-\mu f'(t) + f(t) = kt
\]
which models a forced oscillation in a damping material.  For example, imagine moving your hand back and forth underwater.  Write this equation as a set of coupled first order equations by doing the following:
\begin{itemize}
    \item Define a new function $g=f'(t)$.  This gives you one of the two coupled equations.
    \item Use the given ODE, $g$, and its derivatives to write the second first order equation.
    \item Both of these equations together are now a system of coupled first order equations (which are much easier to solve).
\end{itemize}




\end{document}  