%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article} %report allows for chapters
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{preamble}

\begin{document}

\begin{center}
   \textsc{\large MATH 272, Worksheet 4}\\
   \textsc{Surfaces, volumes, parameterization, and integration}
\end{center}
\vspace{.5cm}

\begin{problem}
    For the following scalar fields $f$, decide whether the level set is a surface or not. If the level set is a surface, what portions (if any) can be described as a graph $z=g(x,y)$?  What about as graphs $y=h(x,z)$ or $x=p(y,z)$? Plot after your analysis to see if your predictions are correct.
    \begin{enumerate}[(a)]
        \item $f(x,y,z)=xyz$ with $C=1$.
        \item $f(x,y,z)=xyz$ with $C=0$.
        \item $f(x,y,z) = z(x-y)+z(e^x-e^y)$ with $C=1$.
        \item $f(x,y,z) = z + \cos(xy)$ with $C=0$.
        \item $f(x,y,z) = z\sin(x)\sin(y)\sin(z)$ with $C=1$.
    \end{enumerate}
\end{problem}

\begin{problem}
    For the sets above that do indeed describe surfaces, find the surface normal $\unitvec$ and the area form $d\Sigma$.
\end{problem}

\begin{problem}
    Consider the surface of the unit cube in $\R^3$ which we'll call $\Sigma$.  Does the normal $\unitvec$ and the area form $d\Sigma$ change in smooth way as we move along the cube?  What is the (right handed) area form on each portion of the cube? Is there a well defined $\unitvec$ along edges or corners? Why does this not matter when we consider the total flux of some vector field $\vecfieldV$,
    \[
        \iint_\Sigma \vecfieldV \cdot \unitvec d\Sigma?
    \]
\end{problem}

\begin{problem}
    Consider the surface defined by the graph of $z = \sqrt{1-x^2-y^2}$ for $x^2+y^2\leq 1$. Become familiar with this example!
    \begin{enumerate}[(a)]
        \item Plot this surface.
        \item Plot the image of following curves \underline{on the surface $\Sigma$}. 
        \begin{itemize}
            \item $\curvegamma_1(t) = \begin{pmatrix} t\\ 0 \end{pmatrix}$.
            \item $\curvegamma_2(t) = \begin{pmatrix} 0 \\ t \end{pmatrix}$. 
            \item $\curvegamma_3(t) = \begin{pmatrix} \frac{1}{2} \cos(t) \\ \frac{1}{2} \sin(t) \end{pmatrix}$.
        \end{itemize}
        Which (if any) correspond to a line of longitude or a line of latitude?
        \item Find an equation for the tangent plane at the point $(0,0,1)$.
        \item Note that the point $(0.1,0.1,1)$ is on this tangent plane.  How close is this point to corresponding point on the sphere? That is, how close is $(0.1,0.1,1)$ to the point $(0.1,0.1,\sqrt{1-(0.1)^2-(0.1)^2})$? Is the tangent plane a reasonable approximation? What if instead we take $(0.01,0.01,1)$ instead?
        \item Find the surface normal $\unitvec$.
        \item What is the area form $d\Sigma$?
        \item Set up an integral that computes the surface area of $\Sigma$.
        \item Set up an integral that computes the total flux of the vector field $\vecfieldV(x,y,z) = \begin{pmatrix} yz \\ xz \\ xy \end{pmatrix}$ through the surface.
    \end{enumerate}
\end{problem}

\begin{problem}
    Consider the surface defined by the graph of $z=\sin(x)\sin(y)$ for $0\leq x \leq \pi$ and $0\leq y\leq \pi$. 
    \begin{enumerate}[(a)]
        \item Consider as well the curve $\curvegamma(t) = \begin{pmatrix} t \\ t \end{pmatrix}$.  What is the area under the curve if we take its image on the surface?
        \item Find the area form $d\Sigma$.
        \item If we have as well a scalar function $f(x,y,z)=x^2+y^2+z^2$, compute the integral
        \[
        \iint_\Sigma f d\Sigma.
        \]
    \end{enumerate}
\end{problem}

\begin{problem}
    Our surfaces have been frozen in time.  However, essentially every physical phenomenon evolves over time.  There are a few ways surfaces arise when time is involved.  Let us consider two examples.
    \begin{enumerate}[(a)]
        \item Consider the two variable scalar field $T(x,t) = \sin(x)e^{-t}$ with $0\leq x \leq L$ and $t\geq 0$. 
        \begin{itemize}
            \item Show that this function satisfies $\left(-\frac{\partial^2}{\partial x^2} + \frac{\partial}{\partial t}\right) T(x,t)=0$. This is known as the 1-dimensional heat equation. Here $T(x,t)$ models the temperature of point $x$ at time $t$ on a rod of length $L$.
            \item Plot the graph $z=T(x,t)$ for $0\leq x \leq L$ and $t\geq 0$.  What can we say about the temperature of the rod as $t\to \infty$?
        \end{itemize}
        \item Consider the three variable scalar field $u(x,y,t) = \sin(mx)\sin(ny)\sin(t)$ with $0\leq x \leq \pi$, $0\leq y \leq \pi$, $t\geq 0$, and $m$ and $n$ are positive integers.
        \begin{itemize}
            \item Show that this function satisfies $\left(-\frac{\partial^2}{\partial x^2}-\frac{\partial^2}{\partial y^2} + \frac{\partial^2}{\partial t^2}\right)u(x,y,t) = 0.$ This is known as the 2-dimensional wave equation. Here, $u(x,y,t)$ models the height of a membrane at the point $(x,y)$ and time $t$.
            \item Plot the graph of the surface $u(x,y,t_0)$ for various values of $t_0$, $m$ and $n$.  Or, visit \url{https://www.geogebra.org/3d/y55rd83m} to have full freedom with this surface (and watch it move over time).
        \end{itemize}
    \end{enumerate}
\end{problem}

\begin{problem}
Compute the flux of the vector fields given in Problem 1 through the following surfaces.
\begin{multicols}{2}
\begin{enumerate}[(a)]
    \item $\Sigma_1$ is the unit square in the $xy$-plane.  
    \item $\Sigma_2$ is the unit square in the $xz$-plane.
    \item $\Sigma_3$ is the unit square in the $yz$-plane.
    \item $\Sigma_4$ is the surface of the unit cube.
\end{enumerate}
\end{multicols}
\end{problem}

\begin{problem}
    Compute the integral of the scalar fields given in Problem 7 over the following regions.
  \begin{multicols}{2}
  \begin{enumerate}[(a)]
      \item $\Omega_1$ is the unit cube.
      \item $\Omega_2$ is the unit cube along with the rectangular prism given by $2<x<3$, $2<y<4$, and $-1<z<1$.
      \item $\Omega_3$ is the portion of the unit cube left over after slicing diagonally by the plane given by the equation $x+y+z=\frac{1}{2}$. Specifically, take the region left \underline{under} the plane and in the unit cube.
  \end{enumerate}
  \end{multicols}  
\end{problem}

\begin{problem}
Compare the result for integrating $\vecfieldU$ from Problem 1 around $\curvegamma_1$ from Problem 8 with computing the flux of the curl of $\vecfieldU$ through $\Sigma_1$ from Problem. That is, check to see
\[
\int_{\curvegamma_1} \vecfieldU \cdot d\curvegamma_1 \stackrel{?}{=} \iint_{\Sigma_1} \left(\grad \times \vecfieldU \right)\cdot \unitvec d\Sigma_1.
\]
\emph{This result is typically referred to as Stokes' theorem. It is another way of relating an integral in a region to an integral along its boundary.}
\end{problem}

\begin{problem}
    Consider a description of the plane $\R^2$ in both Cartesian coordinates $(x,y)$ and polar coordinates $(r,\theta)$.  Recall the coordinate transformations
    \begin{align*}
        x(r,\theta)&= r\cos \theta\\
        y(r,\theta)&= r\sin \theta.
    \end{align*}
    Let $f(x,y) = \frac{1}{\sqrt{1-x^2-y^2}}$ and let us attempt to integrate
    \[
    \iint_{\Sigma} f(x,y)d\Sigma,
    \]
    where $\Sigma$ is the unit disk defined by $x^2+y^2\leq 1$.
    \begin{enumerate}[(a)]
        \item Convert $f(x,y)$ in Cartesian coordinates to a function $f(r,\theta)$ in polar coordinates.
        \item Note that we can convert the area form $d\Sigma=dxdy$ in Cartesian coordinates to an area form in polar coordinates.  Think of the function
        \[
        \vec{\textrm{Pol}}(r,\theta) = \begin{pmatrix} x(r,\theta) \\ y(r,\theta) \end{pmatrix},
        \]
        as the function that coverts Cartesian coordinates into polar coordinates.  Then, 
        \[
        [J]_{\vec{\textrm{Pol}}} = \begin{pmatrix} \frac{\partial x}{\partial r} & \frac{\partial x}{\partial \theta} \\ \frac{\partial y}{\partial r} & \frac{\partial y}{\partial \theta} \end{pmatrix},
        \]
        is the Jacobian of this transformation. The magnitude of determinant of a matrix describes the stretching that the matrix does to the space at a point, and thus the magnitude of the determinant will be a function that depends on each point that describes the local stretching behavior.
        
        Compute $[J]_{\vec{\textrm{Pol}}}$ and compute the determinant of this matrix as well. Simplify this expression as much as possible.
        \item Now, to find the area form in polar coordinates, we simply take
        \[
        \left|\det\left([J]_{\vec{\textrm{Pol}}}\right)\right|drd\theta.
        \]
        Confirm that you have the area form $rdrd\theta$.
        \item Draw a picture of a small segment (sides $dr$ and $d\theta$) in the plane.  Can you see why the area of this segment depends on the radius? Can you also see why it does \underline{not} depend on the angle?
        \item We know we have this correct if 
        \[
        \int_{0}^{2\pi} \int_0^R rdrd\theta = \pi R^2,
        \]
        since this is the area contained inside a circle of radius $R$.  Show that the above integral is true.
        \item Now, set up the integral posed initially in polar coordinates and evaluate this integral using a change of variables (\underline{do not use WolframAlpha}).
    \end{enumerate}
\end{problem}

\vspace*{1cm}
\begin{problem}
    Repeat a very similar argument to show that the volume element $d\Omega$ in cylindrical coordinates is $\rho d\rho d\theta dz$.  \emph{Hint: The coordinate transformations for $x$ and $y$ are analogous.  But, we have the addition of the $z$-coordinate, but this is identical to the Cartesian $z$-coordinate.}
\end{problem}

\vspace*{1cm}
\begin{problem}
Provide an explicit or implicit description (both if possible) of the following regions in $\R^3$ in Cartesian coordinates, cylindrical coordinates, and spherical coordinates.
    \begin{enumerate}[(a)]
        \item A solid box with side lengths $a$, $b$, and $c$.
        \item A solid cylinder of height $h$.
        \item A solid ball of radius $R$.
    \end{enumerate}
\end{problem}

\vspace*{1cm}
\begin{problem}
Likewise, provide an explicit or implicit description (both if possible) of the following surfaces in $\R^3$ in Cartesian coordinates, cylindrical coordinates, and spherical coordinates.
    \begin{enumerate}[(a)]
        \item A the surface of a box with side lengths $a$, $b$, and $c$.
        \item A the surface of a cylinder of height $h$ including endcaps.
        \item A the surface of a ball of radius $R$ (i.e., the sphere).
    \end{enumerate}
\end{problem}

\vspace*{1cm}
\begin{problem}
One can also take a look at curves in each coordinate system.  Plot the following curves by hand. Play around with different choices of parameterizations. Hold certain variables constant. See how this affects your curve!
\begin{enumerate}[(a)]
    \item $x(t)=t$, $y(t)=t$, $z(t)=t$.
    \begin{itemize}
        \item What happens if we hold $x(t)=C$ constant? 
        \item What if we held both $x(t)=C_1$, and $y(t)=C_2$ constant?
        \item Choose some other functions (including constants) for $x(t)$, $y(t)$, and $z(t)$, and plot these as well.
    \end{itemize}
    \item $\rho(t)=t$, $\theta(t)=t$, $z(t)=t$.
    \begin{itemize}
        \item What happens if we hold $\rho(t)=C$ constant? 
        \item What if we held both $\rho(t)=C_1$, and $\theta(t)=C_2$ constant? Or held $\rho(t)$ and $z(t)$ constant?
        \item Choose some other functions (including constants) for $\rho(t)$, $\theta(t)$, and $z(t)$, and plot these as well.
    \end{itemize}
    \item $r(t)=t$, $\theta(t)=t$, $\phi(t)=t$.
    \begin{itemize}
        \item What happens if we hold $r(t)=C$ constant? 
        \item What if we held both $r(t)=C_1$, and $\theta(t)=C_2$ constant? Or held $r(t)$ and $\phi(t)$ constant?
        \item Choose some other functions (including constants) for $\rho(t)$, $\theta(t)$, and $z(t)$, and plot these as well.
    \end{itemize}
    \item ** Find a parameterization of a straight line passing through a point $(x_0,y_0,z_0)$ in cylindrical and spherical coordinates. \emph{Hint: This isn't too hard in those coordinate systems if the curve passes through the origin. But, it can be a bit difficult otherwise!}
\end{enumerate}
\end{problem}

\vspace*{1cm}
\begin{problem}
Integrate the following functions in their relevant coordinate systems over the given region $\Omega$.
\begin{enumerate}[(a)]
    \item $f(x,y,z) = xy+yz$ over $\Omega$ which is the solid unit cube.
    \item $f(\rho,\theta,z) = \frac{z}{\rho}\sin(\theta)$ over $\Omega$ which is the cylinder of radius $1$ and of height $2$. Align this cylinder so the $z$-axis runs through the core of the cylinder and so the height is split at the $xy$-plane.
    \item $f(r,\theta,\phi) = \frac{1}{r^2}\sin(\theta)\sin(\phi)$ over the unit ball centered at the origin.
\end{enumerate}
\end{problem}

\end{document}
