\documentclass{article}
\usepackage{termcal}
\usepackage{xcolor,soul}

% Few useful commands (our classes always meet either on Monday and Wednesday 
% or on Tuesday and Thursday)

\newcommand{\MTWFClass}{%
\calday[Monday]{\classday} % Monday
\calday[Tuesday]{\classday} % Tuesday
\calday[Wednesday]{\classday} % Wednesday
\skipday % Thursday (no class)
\calday[Friday]{\classday} % Friday 
\skipday\skipday % weekend (no class)
}

\newcommand{\TRClass}{%
\skipday % Monday (no class)
\calday[Tuesday]{\classday} % Tuesday
\skipday % Wednesday (no class)
\calday[Thursday]{\classday} % Thursday
\skipday % Friday 
\skipday\skipday % weekend (no class)
}

\newcommand{\Holiday}[2]{%
\options{#1}{\noclassday}
\caltext{#1}{#2}
}

\begin{document}
\begin{center}
   \textsc{\large MATH 272 Calendar}\\
   \textsc{Spring 2021}
\vspace{.5cm}

\begin{calendar}{1/18/2021}{16} % Semester starts on 1/11/2010 and last for 16
                    % weeks, including finals week
\setlength{\calboxdepth}{.3in}
\MTWFClass
% schedule
\caltexton{1}{First day, review. Functions in higher dimensions.}
\caltextnext{Curves and velocity/acceleration vectors.}
\caltextnext{Scalar Fields and partial differentiation.}
\caltextnext{Vector fields and the directional derivative. Gradient.}
\caltextnext{Cont.}
\caltextnext{Divergence and curl of vector fields. Jacobian. Laplacian.}
\caltextnext{\textcolor{red}{\textbf{Homework 1 due.}} Cont.}
\caltextnext{Integration over curves.}
\caltextnext{Cont.}
\caltextnext{Potential functions and conservation.}
\caltextnext{\textcolor{red}{\textbf{Quiz 1.}}}
\caltextnext{\textcolor{red}{\textbf{Homework 2 due.}} Surfaces. Implicit and explicit parameterizations.}
\caltextnext{Tangent planes and normals.}
\caltextnext{Integration over surfaces.}
\caltextnext{\textcolor{red}{\textbf{Homework 3 due.}} Volume integrals.}
\caltextnext{Cont.}
\caltextnext{Cylindrical coordinates.}
\caltextnext{Cont.}
\caltextnext{\textcolor{red}{\textbf{Quiz 2. Homework 4 due.}} Spherical coordinates.}
\caltextnext{Cont.}
\caltextnext{Open.}
\caltextnext{\textcolor{red}{\textbf{Oral Exam 1.}}}
\caltextnext{\textcolor{red}{\textbf{Oral Exam 1.}}}

\caltextnext{Higher dimensional ODEs.}
\caltextnext{Cont.}
\caltextnext{Continuum limit and partial differential equations.}
\caltextnext{\textcolor{red}{\textbf{Homework 5 due.}} Example equations: Laplace/ Poisson's/ heat/ wave equation.}
\caltextnext{Cont.}
\caltextnext{Time dependent Sch\"odinger equations. Superposition states.}
\caltextnext{Cont.}
\caltextnext{\textcolor{red}{\textbf{Quiz 3. Homework 6 due.}} Cont.}
\caltextnext{Maxwell's equations.}
\caltextnext{Cont.}
\caltextnext{PDEs in other coordinate systems.}
\caltextnext{\textcolor{red}{\textbf{Homework 7 due.}} Cont.}
\caltextnext{Open.}
\caltextnext{Open.}
\caltextnext{\textcolor{red}{\textbf{Oral Exam 2.}}}
\caltextnext{\textcolor{red}{\textbf{Oral Exam 2.}}}


\caltextnext{Complex functions, phase.}
\caltextnext{Function spaces and inner products.}
\caltextnext{Symmetries of inner products.}
\caltextnext{\textcolor{red}{\textbf{Homework 8 due.}} Orthonormal bases and projection.}
\caltextnext{Series and integrals as linear combinations.}
\caltextnext{Linear operators and adjoints.}
\caltextnext{Differential operators and domains.}
\caltextnext{\textcolor{red}{\textbf{Quiz 4. Homework 9 due.}} Orthonormal bases of functions.}
\caltextnext{Spectra of differential and Hermitian operators.}
\caltextnext{Fourier series.}
\caltextnext{Cont.}
\caltextnext{\textcolor{red}{\textbf{Homework 10 due}}. Fourier transforms.}
\caltextnext{Dirac delta and fundamental solutions.}
\caltextnext{Cont.}
\caltextnext{Applications.}
\caltextnext{\textcolor{red}{\textbf{Quiz 5. Homework 11 due}}. Cont.}


\caltextnext{Project and review.}
\caltextnext{Project and review.}
\caltextnext{\textcolor{red}{\textbf{Oral Exam 3}}}
\caltextnext{\textcolor{red}{\textbf{Oral Exam 3}}}


% Holidays
\Holiday{1/18/2021}{\textcolor{blue}{Martin Luther King Day.}}
\Holiday{4/12/2021}{\textcolor{blue}{Spring Break.}}
\Holiday{4/13/2021}{\textcolor{blue}{Spring Break.}}
\Holiday{4/14/2021}{\textcolor{blue}{Spring Break.}}
\Holiday{4/16/2021}{\textcolor{blue}{Spring Break.}}

\end{calendar}
\end{center}
\end{document}