%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article} %report allows for chapters
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{preamble}

\begin{document}

\begin{center}
   \textsc{\large MATH 272, Homework 4}\\
   \textsc{Due February 28$^\textrm{th}$}
\end{center}
\vspace{.5cm}

\begin{problem}
Plot the following curves and print pictures of each using GeoGebra.  
\begin{enumerate}[(a)]
	\item (Helix) $\gamma_1(t) = \begin{pmatrix} 3\cos(t) \\ 3\sin(t) \\ t\end{pmatrix}$, from $t=0$ to $t=2\pi$. Where might this show up? If you think about the Earth moving through space and Moon orbiting Earth, then the Moon follows a (locally) helical path.
	
	\item (Falling Ball) $\gamma_2(t) = \begin{pmatrix} t\\  0.5t \\ 9-t^2 \end{pmatrix}$ from $t=0$ to $t=3$.
	
	\item (Perturbed Orbiter) $\gamma_3(t) = \begin{pmatrix} 3\cos(t) \\ 3 \sin(t) \\ \sin(10t)\end{pmatrix}$ from $t=0$ to $t=2\pi$.
	
	\item Create your own curve.
\end{enumerate}
\end{problem}

\begin{problem}
The length of a curve is an important notion. In fact, the length of a curve is often related to the energy of some configuration. We can compute the length of a curve over the time $t=t_0$ to $t=t_1$ by integrating the \emph{speed} of the curve over that time.  That is,
\[
l(\gamma) = \int_{t_0}^{t_1} \|\gamma'(t)\| dt.
\]
We can compute the \emph{energy} of a curve by taking
\[
E(\gamma) = \int_{t_0}^{t_1} \frac{1}{2} \| \gamma'(t)\|dt.
\]
\begin{enumerate}[(a)]
	\item Find the length of the Helix from Problem 1 (a).
	\item Find the energy of the Perturbed Orbiter in Problem 1 (c).  Roughly, this corresponds to the potential energy a rubber band stretched this way would have.
\end{problem}

\begin{problem}
Given a scalar field of two variables $F(x,y)$, we can create an object called the \emph{graph} of $F(x,y)$ by plotting the set of points $(x,y,F(x,y))$. In fact, you have done this many times in your life. For example, you have consistently plotted the graph of a function $f(x)$ by plotting $(x,f(x))$ in the plane!  

Using GeoGebra, plot the graph of the following functions. Print these off and include them.  Also, describe the what the graph of the function does as we move along the $x$-axis, the $y$-axis, and along the line $y=x$. For each, use the range $-3\leq x \leq 3$ and $-3\leq y \leq 3$.
\begin{enumerate}[(a)]
	\item $F(x,y) = \frac{4xy}{1+x^2+y^2}$.
	\item $G(x,y) = \sin(xy)$.
	\item $H(x,y) = \frac{-x^2-y^2}{5}$.
\end{problem}

\begin{problem}
temperature problem.
\end{problem}

\begin{problem}
Another curve problem. Maybe integrate along a scalar? idk
\end{problem}

\end{document}