One application for the work we have done thus far is with the Calder\'on inverse problem. This problem stems from a physical question asked by Alberto Calder\'on in which he asked how much information of a body can we determine from measurements along the boundary of the body. More specifically, by applying a voltage to the boundary and measuring the outgoing current flux, can we determine the conductivity of the body? This is the Electrical Impedance Tomography (EIT) problem.

The more modern formulation of this problem casts it as a geometrical inverse problem by replacing the boundary data with the Dirichlet-to-Neumann map (i.e., the voltage-to-current map) and replacing the conductivity with a Riemannian metric. This has lead to generalizations using differential forms\todo{sources}. 


\subsection{Forward problem}

\subsubsection{Classical EIT}
In the EIT problem, we begin with a region $M$ with unknown symmetric positive definite conductivity matrix $\sigma$. We apply a static scalar potential $\phi$ on $\boundary$ which produces the scalar potential $u$ in the interior. We assume $M$ is flat so that we can choose $g_{ij}=\delta_{ij}$ globally; or, in other words we are working over $\G_n(M)$ where each geometric tangent space is Euclidean $C\ell(T_xM, |\cdot|)$. Then, we posit that $M$ is built from Ohmic material in order to satisfy Ohm's law 
\begin{equation}
\label{eq:ohms_law}
-\sigma \grad \wedge u= \blade{j}
\end{equation}
where $\blade{j}$ is the current density vector field. The conservation law
\begin{equation}
\label{eq:conservation_law}
\int_{\boundary} \blade{j} \cdot \blade{\nu} \omega_\partial = \int_{\boundary} \projection_{\blade{I}_\partial}(\blade{j}^\perp) \cdot dX_{n-1} = 0,
\end{equation}
implies $\grad \cdot \blade{j}= 0$ via Stokes' theorem. Hence, we arrive at the condition on the scalar potential
\begin{equation}
\grad \cdot (\sigma \grad \wedge u) = 0.
\end{equation} 
In other words, the conservation law in \cref{eq:conservation_law} is equivalent to the interior of $M$ being charge free. This is derived more fully in \cite{feldman_calderproblem_nodate}. 

Taking some arbitary basis, conductivity matrix assumes the components $\sigma_{ij}$ for $i,j=1,2,3$.  Via \cite{uhlmann_inverse_2014} in dimension $n>2$, we can realize that the conductivity matrix can be replaced with an intrinsic Riemannian metric with the components in this basis given by
\begin{equation}
\label{eq:conductivity_metric}
    g_{ij} = (\det \sigma^{k\ell} )^{\frac{1}{n-2}} (\sigma^{ij})^{-1}, \quad \sigma^{ij} = (\det g_{k\ell})^{\frac{1}{2}} (g_{ij})^{-1}.
\end{equation}
It is worth noting that these cannot hold in dimension $n=2$. Due to \cref{eq:conductivity_metric}, we can remove the extrinsic need of $\sigma$ with an intrinsic $g$ on the Clifford bundle structure. That is, we are working with $\G(M)$ where each geometric tangent space is given by $C\ell(T_xM,g_x)$. Hence, Ohm's law is given as
\begin{equation}
-\grad \wedge u = \blade{j}.
\end{equation}
Then by \cref{eq:conservation_law}, we find the scalar potential is harmonic
\begin{equation}
\Delta u = 0 \quad \textrm{in $M$}.
\end{equation}



Via Maxwell's equations, it follows that 
\begin{equation}
-\sigma \grad \wedge u^\phi = \grad \cdot b,
\end{equation}
where $b$ is the magnetic bivector field.


\subsubsection{Generalization to forms}

This problem can be cast in a new light by considering harmonic $r$-forms instead of a harmonic 0-form $u$. 
Given some $\varphi \in \Omega^r(\boundary)$, we have the boundary value problem
\begin{equation}
\label{eq:bvp_forms}
\begin{cases} 
\Delta \alpha_r = 0, & \textrm{in $M$}\\
\iota^* \alpha_r = \varphi, \quad \iota^*(\delta \alpha_r) = 0 & \textrm{on $\boundary$}.
\end{cases}
\end{equation}
As stated in \cite{belishev_dirichlet_2008}, there exists a solution $\alpha_r$ to this problem up to a monogenic Dirichlet field $\lambda_D$.

\subsection{Inverse problem}

\subsubsection{Classical EIT}
In the realm of EIT, the Dirichlet data $\phi$ amounts to an input voltage along the boundary and by Ohm's law $\blade{j}=\grad \wedge u$ provides us the current. For any given solution to the boundary value problem, there is the corresponding Neumann data $\projection_{\blade{\nu}}(\grad \wedge u)$. This motivates the so called Voltage-to-Current (VC) operator or  \emph{Dirichlet-to-Neumann (DN) map}
\begin{equation}
\label{eq:classical_dn_map}
\Lambda \phi = \projection_{\blade{\nu}}(\grad u).
\end{equation}
The inverse problem follows.

\vspace*{5pt}
\noindent\textbf{Calder\'on problem.} Let $\Omega$ be an unknown Riemannian manifold with unknown metric $g$ and with known boundary $\Sigma$ and known DN operator $\Lambda$. Can one recover $\Omega$ and the spatial inner product $g$ from knowledge of $\Sigma$ and $\Lambda$?
\vspace*{5pt}

\subsubsection{Generalization to forms}

\todo{belishev sharafutdinov and Shonkwiler sharafutdinov definitions}
Note that the operator $\Lambda$ is often referred to as the \emph{scalar} DN map since the input is the scalar field $\phi$ whereas a more general operator on differential $r$-forms has been described in \cite{belishev_dirichlet_2008,sharafutdinov_complete_2013}. There, we begin with equation \cref{eq:bvp_forms}. The DN map is extended to $r$-forms by
\begin{equation}
\Lambda \varphi = \iota^* (\star d \alpha_r).
\end{equation}
In terms of the multivector equivalent $A_r$, we find
\begin{equation}
\iota^*(\star d \alpha_r) = \projection_{\blade{I}_\partial} ((\grad \wedge A_r)^\star )\cdot dX_{r}^\dagger
\end{equation}


\subsection{Multivector tomography}

There are two notable related questions that can be stated in terms of multivectors. First, the most natural boundary value problems are 
\begin{equation}
\label{eq:multivector_harmonic_bvp}
\begin{cases}
\Delta A = 0 & \textrm{in $M$},\\
A\vert_{\partial M} = B\vert_{\partial M} & \textrm{on $\partial M$},
\end{cases}
\end{equation}
and
\begin{equation}
\label{eq:multivector_monogenic_bvp}
\begin{cases}
\grad A = 0 & \textrm{in $M$},\\
A\vert_{\partial M} = B\vert_{\partial M} & \textrm{on $\partial M$}.
\end{cases}
\end{equation}
It should be noted that we have
\begin{equation}
A\vert_{\partial M} = \projection_{\blade{I}_\partial}(A) + \rejection_{\blade{I}_\partial}(A)
\end{equation}
in order to consider all boundary values for a multivector. 

\subsection{Recovery}

With the DN operator, we can reconstruct the boundary four current $J$.  On $\Sigma$, we have the gradient $\grad_\Sigma$ inherited from $\grad$ on $\Omega$.  In particular, we have the relationship
\[
\grad_\Sigma \phi = \projection{I_\Sigma}{\grad \phi},
\]
which is accessible with our knowledge of $\phi$ and $\Sigma$. The boundary current is then
\[
\current\vert_{\Sigma} = \grad_\Sigma \phi + \Lambda(\phi).
\]
Though we do not have access to $u^\phi$ directly, we do know that $\Delta u^\phi = \rho$ and as such we have the boundary four current by
\[
J\vert_\Sigma = \Delta u^\phi\vert_\Sigma \gamma_0 + \current\vert_\Sigma
\]
as well as the interior four current $J = \current$ since the interior is free of charges.  Defining the the four vector potential as before, we arrive at the extra equation $\Delta \vectorpotential = \current$ in $\Omega$. Once again define the magnetic bivector field $b=\grad \wedge \vectorpotential$ and we note that Ohm's law implies $\grad \cdot b = -\grad \wedge u^\phi$ in $\Omega$ and so the parabivector field $f=u^\phi + b$ is spatially monogenic since we also have $\grad \wedge b = 0$.  This all holds assuming that we can solve the electromagnetic Neumann boundary value problem
\[
\begin{cases} \Delta A = \current & \textrm{in $\Omega$}\\ A = A_\Sigma & \textrm{on $\Sigma$} \end{cases}
\]
\todo[inline]{Show that we can determine the magnetic potential $A_\Sigma$ on the boundary. This may also show that the two notions of the DN operator are equivalent. That'd be nice.}

\todo[inline]{If we show there is always a unique monogenic conjugate $b$ for any harmonic $u$ then this must be what we are doing here. Is this gauranteed by the Cauchy integral?}

\subsubsection{Ohm's law}
and we arrive at $\Delta u = 0$ for the scalar potential and $\Delta \vectorpotential = \current$ for the magnetic vector potential. In terms of the magnetic field bivector, we have $\grad \cdot b = \current$ and once again by Ohm's law we have $-\grad \wedge u^\phi = \grad \cdot b$. This leads us to consider the parabivector field $f=u+b$. We can note that $f$ is (spatially) monogenic since 
\[
\grad f = 0 ~\iff~ -\grad \wedge u^\phi =  \grad \cdot b ~\textrm{and}~ \grad \wedge b = 0,
\]
is satisfied. We see now that the fact that the body $\Omega$ is ohmic gives us a necessary coupling between the scalar potential and the magnetic field.
The classical forward problem in terms of geometric calculus is given by the following scenario. We have an ohmic $M$ and we find the electrostatic potential $u$ satisfying the Dirichlet problem
\begin{equation}
\label{eq:dirichlet_problem}
\begin{cases} \Delta u^\phi = 0 & \textrm{ in $M$} \\  u^\phi \vert_{\boundary} = \phi & \textrm{ on $\boundary$}. \end{cases}.
\end{equation}



Though briefly we mentioned $\Omega$ as a Riemannian manifold, we now take $\Omega$ to be a region in $\R^n$ for brevity. Using the DN operator, one can define a \emph{Hilbert transform} by
\[
T \phi  = d\Lambda^{-1} \phi,
\]
as in \cite{belishev_dirichlet_2008}. It has yet to be shown that this definition coincides with the definition in \cite{brackx_hilbert_2008}, but there is reason to believe they are related. The classical Hilbert transform on $\C$ inputs a harmonic function and outputs another harmonic function $v$ such that $u+iv$ is holomorphic. Essentially, this translates into finding a conjugate bivector field $b$ to $u^\phi$ such that $u^\phi +b$ is monogenic. First, we require $\phi$ satisfies
\todo[inline]{This statement should come from the lagrangian perspective hopefully.}
\begin{equation}
\label{eq:conjugate_requirement}
\left( \Lambda + (-1)^{n}d\Lambda^{-1}d\right)\phi = 0,
\end{equation}
where $d$ is the exterior derivative on forms. \textcolor{red}{They show how to find the image of this, perhaps I can show what the kernel is.} As shown earlier in Section \ref{subsec:diff_forms}, $d$ amounts to $\grad \wedge$ on the multivector field constituent of a form.  When condition \ref{eq:conjugate_requirement} is met, there exists a \emph{conjugate form} $\epsilon \in \Omega^{n-2}(M)$. As well, $\epsilon$ is also coclosed in that $\delta \epsilon=0$. To retrieve the constituent $(n-2)$-vector $E$, we just note $\epsilon = E \cdot dX_k$. Given Hodge duality, we have a 2-form $\beta$ such that $\star\beta = \epsilon$ and the corresponding bivector $b^\star=E$.  Combining the fields $u^\phi$ and $b$ into the parabivector $f=u^\phi+b \in \G_n^{0+2}(\Omega)$. We then note that $f$ is monogenic if and only if
\[
\grad \wedge u = -\grad \cdot b \qquad \textrm{and} \qquad \grad \wedge b = 0.
\]

\begin{lemma}
Given the fields $u^\phi$ and $b$ as above, the corresponding parabivector field
\[
f=u^\phi +b
\]
is monogenic.
\end{lemma}
\begin{proof}
Let $\star \beta^\psi = \epsilon$ as before and note that 
\begin{equation}
\label{eq:conjugate_belishev}
d u^\phi = \star d \epsilon = \star d \star \beta^\psi,  
\end{equation}
as shown in Theorem 5.1 in \cite{belishev_dirichlet_2008}. The multivector equivalent of the right hand side of Equation \cite{eq:conjugate_belishev} yields
\begin{align*}
(\grad \wedge b^\star )^\star &= [(\grad \cdot b^\dagger) I]^\star\\
    &= [I^{-1} ((\grad \cdot b^\dagger) I)]^\dagger\\
    &= ((\grad \cdot b^\dagger)I)^\dagger I\\
    &= \grad \cdot b^\dagger && \textrm{since $\dagger$ of a vector is trivial}\\
    &= -\grad \cdot b. && \textrm{since $\dagger$ of a bivector is -1}
\end{align*}
\textcolor{red}{Perhaps I should just show this property in the differntial forms section.} Thus, we have $\grad \wedge u + \grad \cdot b = 0$. Since $\epsilon$ is coclosed we have
\begin{align*}
0=\grad \cdot b^\star &= \grad \cdot (I^{-1} b)^\dagger \\
    &= \grad \cdot (b^\dagger I)\\
    &= (\grad \wedge b^\dagger) I\\
  \implies ~0  &= \grad \wedge b.
\end{align*}
\textcolor{red}{Perhaps I should just show this property in the differntial forms section.} Thus $\grad f =0$ and $F$ is monogenic.
\end{proof}

We have shown that conjugate forms give rise to monogenic fields.  We now seek to determine for what boundary conditions $\phi$ we have at our disposal. Let $E^\parallel \coloneqq \projection{I_\Sigma}{E}$, with $I_\Sigma$ the boundary pseudoscalar satisfying $\nu I_\Sigma = I$. Hence by Equation \ref{eq:projection_rejection_vectors} we have $E^\parallel = \rejection_{\nu}(E)$ then in investigating the requirement from Equation \ref{eq:conjugate_requirement} we find the multivector equivalent
\begin{align*}
    (\Lambda + (-1)^n (\grad \wedge) \Lambda^{-1} (\grad \wedge))\phi &= E^\perp + (-1)^n T E^\parallel
\end{align*}
so we arrive at the fact that we must have
\[
E^\perp = (-1)^{n-1} T E^\parallel.
\]
In other words,
\[
T  \rejection_\nu(E)= (-1)^{n-1}\projection{\nu}{E}.
\]
Thus, the Hilbert transform maps tangential components of $\grad u^\phi = E$ to nontangential boundary components on the boundary.

