\documentclass{article}
\usepackage{termcal}

% Few useful commands (our classes always meet either on Monday and Wednesday 
% or on Tuesday and Thursday)

\newcommand{\MTWFClass}{%
\calday[Monday]{\classday} % Monday
\calday[Tuesday]{\classday} % Tuesday
\calday[Wednesday]{\classday} % Wednesday
\skipday % Thursday (no class)
\calday[Friday]{\classday} % Friday 
\skipday\skipday % weekend (no class)
}

\newcommand{\TRClass}{%
\skipday % Monday (no class)
\calday[Tuesday]{\classday} % Tuesday
\skipday % Wednesday (no class)
\calday[Thursday]{\classday} % Thursday
\skipday % Friday 
\skipday\skipday % weekend (no class)
}

\newcommand{\Holiday}[2]{%
\options{#1}{\noclassday}
\caltext{#1}{#2}
}

\begin{document}
\begin{center}
   \textsc{\large MATH 272, Tentative Calendar}\\
   \textsc{Spring 2020}
\vspace{.5cm}

\begin{calendar}{1/20/2020}{16} % Semester starts on 1/11/2010 and last for 16
                    % weeks, including finals week
\setlength{\calboxdepth}{.3in}
\MTWFClass
% schedule
\caltexton{1}{First day, review. Complex functions.}
\caltextnext{Complex functions, phase.}
\caltextnext{\textbf{Homework 0 due.}\\ Hilbert spaces, inner products.}
\caltextnext{Integral inner products, symmetries.}
\caltextnext{Infinite orthonormal bases.}
\caltextnext{Expansion and projection with bases.}
\caltextnext{\textbf{Homework 1 due.}\\ Linear operators.}
\caltextnext{Differential operators.}
\caltextnext{Hermitian operators, spectra.}
\caltextnext{Orthogonal polynomials.}
\caltextnext{\textbf{Homework 2 due.}\\ Orthogonal trigonometric polynomials.}
\caltextnext{Fourier series.}
\caltextnext{Special functions (distributions).}
\caltextnext{Fourier transforms.}
\caltextnext{}
\caltextnext{\textbf{Homework 3 due.}\\ Review.}
\caltextnext{Review.}
\caltextnext{\textbf{Take home Exam 1 due.}\\ Review.}
\caltextnext{\textbf{Exam 1.}}
\caltextnext{Functions in higher dimensions.}
\caltextnext{Curves.}
\caltextnext{Higher dimensional ODEs.}
\caltextnext{\textbf{Homework 4 due.} Scalar fields.}
\caltextnext{Directional and partial derivatives.}
\caltextnext{Integration of scalar fields.}
\caltextnext{Vector fields.}
\caltextnext{\textbf{Homework 5 due.} Gradient operator.}
\caltextnext{Curl and divergence operators.}
\caltextnext{Integration of vector fields.}
\caltextnext{Laplace operator.}
\caltextnext{\textbf{Homework 6 due}. Potential functions.}
\caltextnext{Coordinate systems.}
\caltextnext{Parameterizations.}
\caltextnext{Cylindrical coordinates.}
\caltextnext{Spherical coordinates.}
\caltextnext{\textbf{Homework 7 due.} Review.}
\caltextnext{Review.}
\caltextnext{\textbf{Take home Exam 2 due.} Review.}
\caltextnext{\textbf{Exam 2.}}
\caltextnext{Partial differential equations, separation of variables.}
\caltextnext{Laplace and Poisson's equation.}
\caltextnext{Heat equation.}
\caltextnext{\textbf{Homework 8 due.} Wave equation and Fourier transforms.}
\caltextnext{Schr\"odinger equation with a potential.}
\caltextnext{Time dependent Sch\"odinger equation.}
\caltextnext{}
\caltextnext{\textbf{Homework 9 due.} Maxwell's equations.}
\caltextnext{}
\caltextnext{PDEs in other coordinate systems.}
\caltextnext{Harmonics.}
\caltextnext{Fundamental solutions.}
\caltextnext{\textbf{Homework 10 due.} Review.}
\caltextnext{Review.}
\caltextnext{\textbf{Take home Exam 3 due.} Review.}
\caltextnext{\textbf{Exam 3.}}
\caltextnext{Mini-project: Hydrogen atom.}
\caltextnext{Mini-project: Hydrogen atom.}
\caltextnext{Mini-project: Hydrogen atom.}
\caltextnext{Mini-project: Hydrogen atom.}


% Holidays
\Holiday{1/20/2020}{Martin Luther King Day}
\Holiday{3/16/2020}{Spring Break}
\Holiday{3/17/2020}{Spring Break}
\Holiday{3/18/2020}{Spring Break}
\Holiday{3/20/2020}{Spring Break}

\end{calendar}
\end{center}
\end{document}