\documentclass[doctor]{thesis}
\usepackage{import}
\usepackage{preamble}
\usepackage{environments}
% package for todo 
\setlength{\marginparwidth}{2cm}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage[disable]{todonotes}
\setuptodonotes{size=\scriptsize,backgroundcolor=red!15!white} 

%\usepackage{showkeys} %show cites and refs




% Title Page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% title of your thesis
\title{Approaching Geometric Inverse Problems using Analysis of Multivector Fields}

% author's name
\author{Colin Roberts}

% author's email address
\email{colin.roberts@rams.colostate.edu}

% department name
\department{Department of Mathematics}

% semester of completion
\semester{Spring 2021}

% committee member names
\advisor{Clayton Shonkwiler}
\committee{Henry Adams} % as many committee entries as you need
\committee{Wolfgang Bangerth}
\committee{Jacob Roberts}

% Copyright Page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% here is an example of student copyright declaration
% note that the \copyright command prints the copyright symbol,
% so we use the name \mycopyright instead
\mycopyright{%
Copyright by Colin Roberts 2020 \\
All Rights Reserved
}

%\tableofcontents

\abstract{
The geometrical inverse problem of determining an unknown Riemannian manifold $M$ from the Dirichlet-to-Neumann (DN) map on the boundary is known as the Calder\'on problem and, in dimension two, this problem is solvable up to conformal deformation. One technique is to us the DN map to the algebra of holomorphic functions on the manifold which, by Gelfand, this set is then homeomorphic to the manifold. In higher dimensions, one can replace the complex line bundle with differential forms, but another natural choice is to consider a geometric (or Clifford) algebra bundle whose sections are multivector fields. The graded algebra of multivector fields comes with a natural differential operator known as the gradient (or Dirac) operator that replaces the Hodge-Dirac operator in the exterior algebra of forms. Fields in the kernel of the gradient are monogenic, and these monogenic fields are a natural generalization of holomorphic functions. In this work, we prove a version of the Hodge-Morrey decomposition which splits the space of multivector fields into an orthogonal sum of monogenic fields and gradients. We define a suitable notion of a spectrum of the space of monogenic fields and prove the spectrum to be homeomorphic to the underlying manifold with the weak-$\ast$ topology.
}

% Acknowledgments 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgements{ Fill in acknowledgements here.
}

\begin{document}

\todo{Start working on a literature review type thing so I can cite sources more easily later.}
\todo{The space $\G_n^+$ is a module over $\spingroup$ and in the case of the complex numbers we can realize this is just a phase. Similar thing for quaternions probably.}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\frontmatter % starts preliminary pages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle              % insert title page
\makemycopyright        % insert copyright page
\makeabstract           % insert abstract page
\makeacknowledgements   % insert acknowledgements page

% any extra preliminary pages can be added here
% below is an example of a dedication page
% the dedication page is optional
\prelimtocentry{Dedication} % add table of contents entry
\begin{flatcenter} % center without extra space

    % page title
    DEDICATION

    %\vspace{3em} % place at top
    \vfill % or center on page

    \noindent \textit{I would like to dedicate this thesis to my dog fluffy.}
    \vfill % fill extra space at bottom
\end{flatcenter}
\newpage

\tableofcontents    % insert table of contents
\listoftables       % insert list of tables (optional)
\listoffigures      % insert list of figures (optional)

\mainmatter % starts thesis body

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Chapter 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction}

\section{Introduction}
\input{chapter_1/introduction.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Chapter 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Preliminaries}

\section{Clifford and geometric algebras}
\label{subsec:clifford_and_geometric_algebras}
\input{chapter_2/clifford_and_geometric_algebras.tex}

\section{Geometric manifolds}
\label{sec:geometric_manifolds}
\input{chapter_2/geometric_manifolds.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Chapter 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Analysis of multivector fields}

\section{Spaces of fields}
\label{sec:spaces_of_fields}
\input{chapter_3/spaces_of_fields.tex}

\section{Algebras of fields}
\label{sec:algebras_of_fields}
\input{chapter_3/algebras_of_fields.tex}

\section{Gelfand theory}
\label{sec:gelfand_theory}
\input{chapter_3/gelfand_theory.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Chapter 4
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Inverse problems}

\section{Tomography}
\label{sec:tomography}
\input{chapter_4/tomography.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%
%\section{Conclusion}
%\input{conclusion.tex}
%
%\section{Extras}
%
%Journals:
%\begin{itemize}
%    \item Advances in Applies Clifford Algebras.
%\end{itemize}

% EXTRA STUFF BELOW
%\section{Further questions}
%\input{further_questions.tex}


\bibliographystyle{siam}
\bibliography{calderon_problem}





\end{document}
